### 2018-01-10 master/paper.tex
Update publication list

>>>>

\section*{Domestic Conference}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
    ``Componentized Dynamic Memory Allocator for Embedded Systems,''
    \emph{in Proceedings of IPSJ Kansai-Branch Convention 2017},
    A-3, 2017 (in Japanese).
\item
    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
    ``mruby Bytecode Loader Using Bluetooth in Multi-VM Environment,''
    \emph{in Proceedings of ETNET2016},
    No.8, pp.1-6, 2016 (in Japanese).
\end{enumerate}
